### 2018-10-14 VM524/HW1/tex/submission.tex
20181014

\section{Exercise2}
  Let $X$ and $Y$ be 2 sequences of random numbers, the correlation coefficient of these 2 random variables is calculated as
  \begin{equation}
  	\rho_{XY} = \frac{cov(X, Y)}{\sqrt{E[X^2] E[Y^2]}}
  \end{equation}
  the covariance of $X$ and $Y$ is calculated as
  \begin{equation}
  	cov(X, Y) = E[(X-E[X])(Y-E[Y])] = E[XY] - E[X]E[Y]
  \end{equation}
  With $E[XY], E[X], E[Y], E[X^2], E[Y^2]$ provided, the correlation coefficient can be therefore calculated. And
  numerical experiment has been done with 500 times trial.
   \begin{figure}[H]
	  	\centering
	  	\includegraphics[height=10cm]{CovPlot.png}
	  	\caption{Covariance of random numbers}
	  	\label{img:cov}
  	\end{figure}
\section{Exercise3}

\section{Exercise4}

\end{document}

>>>>

\section{Exercise2}
  Let $X$ and $Y$ be 2 sequences of random numbers, the correlation coefficient of these 2 random variables is calculated as
  \begin{equation}
  	\rho_{XY} = \frac{cov(X, Y)}{\sqrt{E[X^2] E[Y^2]}}
  \end{equation}
  the covariance of $X$ and $Y$ is calculated as
  \begin{equation}
  	cov(X, Y) = E[(X-E[X])(Y-E[Y])] = E[XY] - E[X]E[Y]
  \end{equation}
  With $E[XY], E[X], E[Y], E[X^2], E[Y^2]$ provided, the correlation coefficient can be therefore calculated. And
  numerical experiment has been done with 500 times trial.
   \begin{figure}[H]
	  	\centering
	  	\includegraphics[height=10cm]{CovPlot.png}
	  	\caption{Covariance of random numbers}
	  	\label{img:cov}
  	\end{figure}
\section{Exercise3}
	Assume the angular speed of the motion is $\omega = 4\pi rad/s$, with radius $r = \frac{d}{2} = \frac{l}{2} = 5cm$, the  mean velocity can be calculated as 
	\begin{equation}
		u = \frac{1}{2} \omega  r = 0.1\pi m/s
	\end{equation}
	Thus, the energy input rate is estimated as
	\begin{equation}
		\epsilon \sim \frac{u^3}{l} \approxeq 9.8696\times10^{-1} (m^2 \cdot s^{-3})
	\end{equation}
	With the kinematic viscosity of water taken as $\nu = 1.006\times10^{-6}  (m^2 \cdot s^{-1})$, the Kolmogorov scale is estimated as
	\begin{equation}
		\eta \sim (\frac{\nu^3}{\epsilon})^{\frac{1}{4}} \approxeq 3.187\times10^{-2}mm
	\end{equation}

\section{Exercise4}
	Load the give txt datafile, denote the input 1D data as $u$, then perform FFT on $u$ yields $u^*$. The energy spectrum is calculated as
	$E(k) = \frac{1}{2} u^*(k)^2$ for each $u^*$. The log plot of the energy spectrum is provided.
	\begin{figure}[]
		\centering
		\includegraphics[angle=90, width=12cm]{EnergySpectrum.png}
		\caption{Energy Spectrum}
		\label{img:es}
	\end{figure}
\end{document}

### 2018-10-14 VV556/HW4/submission.tex
20181014

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Methods of Applied Mathematics I\\ HW2 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

@@

\section{Exercis2.1}
	\begin{enumerate}
		\item 
			\begin{proof}
				\begin{equation}
					\begin{aligned}
						RHS & = \frac{1}{4} (||x+y||^2  - ||x-y||^2)\\
						    & = \frac{1}{4} (<x+y, x+y> - <x-y, x-y>)\\
						    & = \frac{1}{4} (<x+y, x> + <x+y, y> - <x-y, x> - <x-y, -y>)\\
						    & = \frac{1}{4} (\overline{<x, x+y>} + \overline{<y, x+y>} - \overline{<x, x-y>} + \overline{<y, x-y>})\\
						    & = \frac{1}{4} (\overline{<x, x>} + \overline{<x, y>} + \overline{<y, x>} + \overline{<y, y>} - \overline{<x, x>} + \overline{<x, y>} + \overline{<y, x>} - \overline{<y, y>})\\
						    & = \frac{1}{2}(\overline{<x,y>} + \overline{<y, x>})\\
						    & = \frac{1}{2}(<x, y> + <y, x>)\\
						    & = <x, y> = LHS
					\end{aligned}
				\end{equation}
				The last line is valid as the inner-product is defined on real space s.t. $<x, y>=<y, x>$.
			\end{proof}
		\item 
			\begin{proof}
				As have been proved aboved
				\begin{equation}
					\begin{aligned}
						   & \frac{1}{4} (||x+y||^2  - ||x-y||^2)\\
						=  & \frac{1}{2}(<x, y> + <y, x>)
					\end{aligned}
				\end{equation}
				Also, replace $y$ with $iy$ yields
				\begin{equation}
					\begin{aligned}
						  & \frac{i}{4} (||x+iy||^2  - ||x-iy||^2)\\
						= & \frac{i}{2} (<x, iy> + <iy, x>)\\
						= & \frac{i}{2} (i<x, y> + \overline{i}<y, x>)\\
						= & \frac{1}{2} (-<x, y> + <y,x>)
					\end{aligned}
				\end{equation}
				Thus
				\begin{equation}
					\begin{aligned}
						RHS & = \frac{1}{4} (||x+y||^2  - ||x-y||^2) - \frac{i}{4} (||x+iy||^2  - ||x-iy||^2)\\
						    & = \frac{1}{2}(<x, y> + <y, x>) - \frac{1}{2} (-<x, y> + <y,x>)\\
						    & = <x, y> = LHS
					\end{aligned}
				\end{equation}
			\end{proof}
		\item 
			\begin{proof}
				\begin{equation}
					\begin{aligned}
						LHS & = ||x+y||^2 + ||x-y||^2\\
						    & = <x+y, x+y> + <x-y, x-y>\\
						    & = <x+y, x> + <x+y, y> + <x-y, x> - <x-y, y>\\
						    & = \overline{<x, x+y>} + \overline{<y, x+y>} + \overline{<x, x-y>} - \overline{<y, x-y>}\\
						    & = \overline{<x, x>} + \overline{<x, y>} + \overline{<y, x>} + \overline{<y, y>} + \overline{<x, x>} - \overline{<x, y>} - \overline{<y, x>} + \overline{<y, y>}\\
						    & = 2(<x, x>+<y, y>)\\
						    & = 2(||x||^2 + ||y||^2) = RHS
					\end{aligned}
				\end{equation}
			\end{proof}	
		\item 
			\begin{proof}
				As any norm induced by inner product should satisfy the parallelogram law, it's easy to show that the norm $||.||_\infty : f\mapsto \sup_{x\in [a, b]} |f(x)|$ on $C[a, b]$ can not be induced by any inner product since it does not satisfy the parallelogram law. For example, let
				\begin{equation}
					f(x) = \frac{x-a}{b-a}
				\end{equation}
				and
				\begin{equation}
					g(x) = (\frac{x-a}{b-a})^2
				\end{equation}
				then
				\begin{equation}
					||f+g|| = \max_{x\in[a, b]} |(f+g)(x)| = |(f+g)(b)| = 2
				\end{equation}
				\begin{equation}
					||f-g|| = \max_{x\in[a, b]} |(f-g)(x)| = |(f-g)(\frac{a+b}{2})| = \frac{1}{4}
				\end{equation}
				\begin{equation}
					||f|| = \max_{x\in[a, b]} |f(x)| = |f(b)| = 1
				\end{equation}
				\begin{equation}
					||g|| = \max_{x\in[a, b]} |g(x)| = |g(b)| = 1
				\end{equation}
				It's obvious that
				\begin{equation}
					||f+g||^2 + ||f-g||^2 = \frac{65}{4} \neq 2(||f||^2 + ||g||^2) = 4
				\end{equation}
			\end{proof}

		\item 
			Assume the norm satisfies the parallelogram law, that is
			\begin{equation}
				||x+y||^2 + ||x-y||^2 = 2(||x||^2 + ||y||^2)
			\end{equation}
			Let
			\begin{equation}
				<x, y> \triangleq \frac{1}{4}(||x+y||^2 - ||x-y||^2)
			\end{equation}
			it's left to prove that $<x, y>$ is an inner product.\\
			Firstly, $<x, y+z>$ can be expanded according to the definition as follows
			\begin{equation}
				\begin{aligned}
					<x, y+z> & = \frac{1}{4}(||x+y+z||^2 - ||x-(y+z)||^2)\\
					         & = \frac{1}{4}(||y+z+x||^2 - ||y+z-x||^2)
				\end{aligned}
			\end{equation}
			Since
			\begin{equation}
				||y+z+x||^2 + ||y-z+x||^2 = 2(||y+x||^2 + ||z||^2)
			\end{equation}
			Then
			\begin{equation}
				||y+z+x||^2 = 2(||y+x||^2 + ||z||^2) - ||y-z+x||^2
			\end{equation}
			Swap $y$ and $z$ yields
			\begin{equation}
				||x+y+z||^2 = 2(||z+x||^2 + ||y||^2) - ||z-y+x||^2
			\end{equation}
			Adding the two equations above and divided by 2 yields
			\begin{equation}
				||y+z+x||^2 = ||y||^2 + ||z||^2 + ||x+y||^2 + ||x+z||^2 -\frac{1}{2}(||y-z+x||^2 + ||z-y+x||^2)
			\end{equation}
			Replace $x$ with $-x$
			\begin{equation}
				||y+z-x||^2 = ||y||^2 + ||z||^2 + ||x-y||^2 + ||x-z||^2 -\frac{1}{2}(||y-z-x||^2 + ||z-y-x||^2)
			\end{equation}
			Hence
			\begin{equation}
				||y+z+x||^2 + ||y+z-x||^2 = (||x+y||^2 - ||x-y||^2) + (||x+z||^2 - ||x-z||^2)
			\end{equation}
			As
			\begin{equation}
				<x, y> = \frac{1}{4} (||x+y||^2 - ||x-y||^2)
			\end{equation}
			and
			\begin{equation}
				<x, z> = \frac{1}{4} (||x+z||^2 - ||x-z||^2)
			\end{equation}
			It's therefore can be concluded that
			\begin{equation}
				<x, y+z> = <x, y> + <x, z>
			\end{equation}
			Secondly,

\section{Exercise2.2}
	Denote $c_0 = \{(a_n)_{n\in\mathbb{N}}: \lim\limits_{n \rightarrow \infty} a_n = 0\}$ and $l^1 = \{(b_n)_{n\in\mathbb{N}}: \sum_{n=0}^{\infty} |b_n| \le \infty\}$
	\begin{enumerate}
		\item
		YES
		\begin{proof}
			For any $(a_n) \in c_0$ and $\epsilon > 0$, $\exists N_1$ s.t. when $n > N_1$, $|a_n| \le \frac{\epsilon}{2}$.\\
			Also, a sequence $(b_n) \in l^1$ can be found s.t. $|b_n| \le \frac{\epsilon}{2}$ when $n > N_2$, and $b_n = a_n$ for $n \leq N_3 \triangleq \max(N_1, N_2)$. This does not violate requirement for $(b_n)$ as the sum of $|b_n|$ here is finite.\\
			Thus, $||(a_n) - (b_n)||_\infty = \sup_{n \in \mathbb{N}} |a_n - b_n| \leq |a_n| + |b_n| \leq \frac{\epsilon}{2} + \frac{\epsilon}{2} = \epsilon$ when $n > N_3$. And it implies that $l^1$ is dense in $c_0$ under the $||.||_\infty$ norm.
		\end{proof}
		\item 
		NO
		\begin{proof}
			For example, pick a sequence $(a_n) \in c_0$ s.t. $a_n = \frac{1}{n+1}$, for any sequence $(b_n) \in l^1$. The norm $||(a_n) - (b_n)|| = \sum_{n=0}^{\infty} |a_n - b_n| \geq \sum_{n=0}^{\infty} (|a_n| - |b_n|) = (\sum_{n=0}^{\infty}|a_n|) - (\sum_{n=0}^{\infty}|b_n|)$ diverges as $\sum_{n=0}^{\infty}|a_n|$ goes infinite and $\sum_{n=0}^{\infty}|b_n|$ is finite.
		\end{proof}

>>>>

\title{	
\normalfont \normalsize 
\textsc{Shanghai Jiao Tong University, UM-SJTU JOINT INSTITUTE} \\ [25pt] % Your university, school and/or department name(s)
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\huge Methods of Applied Mathematics I\\ HW4 \\ % The assignment title
\horrule{2pt} \\[0.5cm] % Thick bottom horizontal rule
}

@@

\section{Exercise4.1}
	Let $f(x)$ be extended as
	\begin{equation}
		f(x) = \left\{
			\begin{aligned}
				x(\pi - x) & x\in [2n\pi, (2n+1)\pi] \\
				-x(\pi - x) & x\in [-(2n-1)\pi, 2n\pi] \\
			\end{aligned}
		\right.
	\end{equation}
	Then $f(x)$ is both odd and periodic. Thus fouier-sine series can be employed.
	\begin{equation}
		f(x) = \sum_{n=1}^{\infty} b_n sin(nx)
	\end{equation} 
	Coefficients $b_n$ are calculated by
	\begin{equation}
		\begin{aligned}
			b_n  & = \frac{2}{\pi} \int_{0}^{\pi} f(x) sin(nx) dx \\
				 & = \frac{2}{\pi} \int_{0}^{\pi} x(\pi - x) sin(nx) dx \\
			     & = \frac{4[1-(-1)^n]}{n^3 \pi} \quad \text{(Integrate by parts)}
		\end{aligned}
	\end{equation}
	Thus
	\begin{equation}
		f(x) = \sum_{k=0}^{\infty} \frac{8 sin(2k+1)x}{\pi (2k+1)^3}
	\end{equation}
	Taking $x = \frac{\pi}{2}$ yields
	\begin{equation}
		\sum_{k=0}^{\infty} \frac{(-1)^k}{(2k+1)^3} = \frac{\pi^3}{32}
	\end{equation}

\section{Exercise4.2}
	\begin{enumerate}
		\item 
			\begin{proof}
				The orthogonal property is justified as
				\begin{equation}
					\int_{0}^{\pi} (\frac{1}{\sqrt{\pi}})^2 dx = \frac{1}{\pi} \int_{0}^{\pi} dx = 1
				\end{equation}
				\begin{equation}
					\int_{0}^{\pi} (\sqrt{\frac{2}{\pi}}cos(nx))^2 dx = \frac{2}{\pi} \int_{0}^{\pi} cos^2(nx)dx = 1
				\end{equation}
				\begin{equation}
					\int_{0}^{\pi} \frac{1}{\sqrt{\pi}} \sqrt{\frac{2}{\pi}}cos(nx) dx = 0
				\end{equation}
				\begin{equation}
					\int_{0}^{\pi} \sqrt{\frac{2}{\pi}}cos(nx) \sqrt{\frac{2}{\pi}}cos(mx) dx = \frac{2}{\pi} \int_{0}^{\pi} cos(nx) cos(mx) dx = 0
				\end{equation}
			\end{proof}
		\item 
			\begin{proof}

			\end{proof}

		\item

		\item

		\item

		\item
